---
title: "Activity 11"
author: "Charlene Thomas"
date: "11/21/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Activity - Lab 11

1.Write a function that generates numbers from binomial(n, p) distribution using runif()function. Hint:binomial(n, p) random variable can be defined as a sum of  n independent Bernoulli (p) random variables.

```{r}
set.seed(3)
heads <- function(x, prob) {
  trial <- runif(x, 0, 1)
  sum(trial <= prob)
}

heads(100, 0.5)
rbinom(1,100,0.5)

```

2. Compare performance of your function with rbinom() using microbenchmark() function.

```{r}
library(microbenchmark)

microbenchmark(heads(100, 0.5),
               rbinom(1,100,0.5))

```

3. Suppose we want to simulate data from a linear regression model:Yi= β0 + β1 × Xi +i i= 1,...,N where∼N(0,3) and X is a covariate that ranges between 20 and 40. Let β0= 15 and β1= 0.4 are known coefficients. Generate data (N = 50) from this models with given coefficients. Fit a linear regression model and plot fitted values vs residuals using ggplot() function. Please do not forget to use set.seed() function for reproducibility.

```{r}
library(ggplot2)
set.seed(1231)

e <- rnorm(50, 0, 3)
x <- sample(20:40, 50, replace = TRUE)
b0 <- 15
b1 <- 0.4
y <- b0 + b1*x + e

linear.model <-lm(x ~ y)

ggplot() + 
  geom_point(aes(x = linear.model$fitted.values,  y = linear.model$residuals))
```


4. Box-Muller algorithm: generate U1 and U2 two independent uniform(0, 1) random variables and set: R=√−2 log(U1) and θ= 2πU2thenX=Rcos(θ) and Y=Rsin(θ) are two independent normal variables.

Write a function that generates normal variates using Box-Muller algorithm. Compare simulated data from your function with simulated data fromrnorm()functionusingggplot()(histogram?).

```{r}
box.muller <- function(n) {
  U1 <- runif((n / 2), 0, 1)
  U2 <- runif((n / 2), 0, 1)
R <- sqrt(-2 * log(U1))
theta <- 2 * pi * U2
X <- R * cos(theta)
Y <- R * sin(theta)
list <- c(X, Y)
return(list)
}

muller <- box.muller(1000)

normal <- rnorm(1000, 0, 1)

ggplot() +
  geom_density(aes(normal, fill = "green", alpha = 0.5)) + 
  geom_density(aes(muller, fill = "blue", alpha = 0.5)) +
  guides(alpha = FALSE)

```


